\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{helvet} % Use Helvetica as the sans-serif font
\renewcommand{\familydefault}{\sfdefault} % Use the sans-serif font by default
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}




%Curriculum Vitae Ani Mema - template by: Aline R. Antunes

\begin{document}
\begin{center}
    \textbf{Ani Mema}\\
    Developer
    \end{center}

\begin{center}
    +39 3343459442 \textbullet \ amema@student.42roma.it \textbullet \ linkedin.com/in/animema \textbullet \ github.com/amema42
\end{center}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{42 Roma Luiss} \hfill Rome, Italy

Programming peer-to-peer and Project-based school, part of the international 42 Network\hfill 2023 - 2024

Relevant Coursework: Advanced C and Systems Programming, Algorithms and Data Structures, Network Programming, Unix/Linux Systems, Software Development Projects

\vspace{12pt}

\textbf{UniTO} \textit{Computer Science} \hfill Turin, Italy

Bachelor's Degree in Computer Science \hfill	2020 – ongoing

\vspace{12pt}

\textbf{Liceo G. D. Cassini } \hfill	Sanremo, Italy

Scientific High School - "Indirizzo Scientifico, Scuola Superiore di Secondo Grado"\hfill 2013 - 2019

\vspace{12pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Club Tenco} \textit{- Non-profit association in Music Industry} \hfill Sanremo, Italy and Remote

\textbf{Event Production} \hfill 10/2018 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Specialized in event production, leading teams through planning, coordination, and execution.
    \item Developed skills in team collaboration, organizational leadership, event management step-by-step execution.
    \item Managed organization's web presence, social media platforms and company's digitalization with different projects.
\end{itemize}

\vspace{12pt}

\textbf{iCompany} \hfill Rome, Italy

\textbf{Support event production} \hfill 04/2023 - 05/2023

Collaboration in event production for the "1 May Concert"\ handling logistical coordination, team collaboration, and seamless execution of components.
\vspace{12pt}

\textbf{Aquagift} \textit{- Startup}\hfill Rome, Italy

\textbf{Co-Founder \& CTO} \hfill 05/2023 - On Hold

Developed within LVenture and LUISS, aims to provide free water by covering costs through advertising, emphasizing sustainability and ensuring access to essential resources. As CTO, I lead technical and marketing strategies to achieve our mission:



\begin{itemize}[noitemsep,topsep=0pt]
    \item Spearheading sustainable technology solutions and strategies to ensure mission alignment with sustainability principles and resource accessibility.
    \item Leading comprehensive technical and marketing strategy development and execution.

\end{itemize}
\textbf{Other experiences/ projects:} Studi Medici Lagrange, IT Support (Turin, 2022) - Leonardo \& 42 Roma Luiss - WebApp project (2024, Rome)  - For further insights into my work, please visit my GitHub profile.\hfill

\begin{center}
    \textbf{Technical}
\end{center}

\textbf{Programming Languages}: \
C, C++, JavaScript, HTML, CSS, JavaScript, familiar with Python

\textbf{Framework \& DBMS}: \
React.js, Node.js, Express.js, PostgreSQL, MySQL, familiar with Angular

\textbf{Technologies, Software \& Tools}: \
Git, Linux systems, Docker, Pandas, AWS, Adobe Suite (Ps, Ai, Id, Pr), Adobe XD, Figma, Notion, Miro, WordPress, Shopify, Microsoft Suite (Excel)


\vspace{12pt}

\begin{center}
    \textbf{Skills}
\end{center}
\textbf{Languages:} Italian (native), English (business fluent/advanced), Albanian (native)

\textbf{Skills \& Interests:} Solid background in scientific thinking and CS, I have acquired expertise in web and software development, marketing analytics, UX/UI design, product design, and IT project management. Proficient in SAP, using creativity for solutions and analytical thinking for data-driven insights and process optimization.


\end{document}
